Lossy compression of DNA sequencing quality data

### 2016-05-26 bmc_manuscript/manuscript.tex
small tweak

As a measure of compression effectiveness, which reflects the sum of
fixed and marginal costs, we use bits/base-call, defined as the size
of the compressed representation of quality values (in bits) divided
by the number of quality values represented. As measures of
information loss we use three loss functions following previous
work~\cite{Malysa01102015}: mean squared error (\textsc{mse}), defined
as $\frac{1}{n}\sum_{i=1}^{n}{(Q_i'-Q_i)^2}$; mean absolute deviation
(\textsc{mad}), defined as $\frac{1}{n}\sum_{i=1}^{n}{|Q_i'-Q_i|}$;
and mean of the values derived from the Cauchy--Lorentz distribution
(mean Cauchy--Lorentz loss), defined as
$\frac{1}{n}\sum_{i=1}^{n}{log_{2}(1 + |Q_i'-Q_i|)}$, where $n$ is the
number of quality values, $Q_i'$ is the compressed/decompressed
quality value, and $Q_i$ is the original quality value associated with
position $i$.

>>>>

As a measure of compression effectiveness, which reflects the sum of
fixed and marginal costs, we use bits/base-call, defined as the size
of the compressed representation of quality values (in bits) divided
by the number of quality values represented. As measures of
information loss we use three loss functions following previous
work~\cite{Malysa01102015}: mean squared error (\textsc{mse}), defined
as $\frac{1}{n}\sum_{i=1}^{n}{(Q_i'-Q_i)^2}$; mean absolute deviation
(\textsc{mad}), defined as $\frac{1}{n}\sum_{i=1}^{n}{|Q_i'-Q_i|}$;
and mean of the values derived from part of the formula defining the
Cauchy--Lorentz distribution (mean Cauchy--Lorentz loss), defined as
$\frac{1}{n}\sum_{i=1}^{n}{log_{2}(1 + |Q_i'-Q_i|)}$, where $n$ is the
number of quality values, $Q_i'$ is the compressed/decompressed
quality value, and $Q_i$ is the original quality value associated with
position $i$.
